---
title: "JSON Web Tokens (JWT) and Keys (JWK) in R"
date: "`r Sys.Date()`"
output:
  html_document
vignette: >
  %\VignetteIndexEntry{JSON Web Tokens (JWT) and Keys (JWK) in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = "")
```

Javascript Object Signing and Encryption (JOSE) consists of a set of specifications for encryption and signatures based on the popular JSON format. This is work in progress, the IETF [jose workgroup](https://tools.ietf.org/wg/jose) usually has the latest information. 

 - [RFC7515](https://tools.ietf.org/html/rfc7515): JSON Web Signature (JWS)
 - [RFC7516](https://tools.ietf.org/html/rfc7516): JSON Web Encryption (JWE)
 - [RFC7517](https://tools.ietf.org/html/rfc7517): JSON Web Key (JWK)
 - [RFC7518](https://tools.ietf.org/html/rfc7518): JSON Web Algorithms (JWA)
 - [RFC7519](https://tools.ietf.org/html/rfc7519): JSON Web Token (JWT)
 
The `jose` package implements some of these specifications, in particular for working with JSON web tokens and keys.

### JSON Web Tokens (JWT)

The most common use of JSON Web Tokens is combining a small payload (the 'claim') with a HMAC tag or RSA/ECDSA signature. See also [https://jwt.io](https://jwt.io) for short introduction. 

```{r}
library(openssl)
library(jose)

# Example payload
claim <- jwt_claim(user = "jeroen", session_key = 123456)

# Encode with hmac
key <- charToRaw("SuperSecret")
(jwt <- jwt_encode_hmac(claim, secret = key))

# Decode 
jwt_decode_hmac(jwt, secret = key)
```

The decoding errors if the tag verification fails.

```{r error=TRUE}
# What happens if we decode with the wrong key
jwt_decode_hmac(jwt, secret = raw())
```

Similalry, we can use an RSA or ECDSA key pair we to verify a signature from someone's public key.

```{r}
# Generate ECDSA keypair
key <- ec_keygen()
pubkey <- as.list(key)$pubkey

# Sign with the private key
(jwt <- jwt_encode_sig(claim, key = key))

# Decode and verify using the public key
jwt_decode_sig(jwt, pubkey = pubkey)
```

Again decoding will error if the signature verification fails.

```{r error = TRUE}
wrong_key <- ec_keygen()
jwt_decode_sig(jwt, pubkey = wrong_key)
```


The spec also describes methods for encypting the payload, but this is currently not widely in use yet.

### JSON Web Keys (JWK)

JOSE also specifies format for exchanging RSA/EC/AES keys in [RFC7517](https://tools.ietf.org/html/rfc7517) in JSON format. The `jose` package seamlessly imports/exports this format for use with the JWT functions above or anything else in the `openssl` package.



```{r}
library(openssl)
library(jose)

# Generate a ECDSA key
key <- openssl::ec_keygen()
jsonlite::prettify(write_jwk(key))

# Use public key
pubkey <- as.list(key)$pubkey
json <- write_jwk(pubkey)
jsonlite::prettify(json)

# Read JWK key
(key2 <- read_jwk(json))
identical(key, key2)
```
