---
title: "Reading/Writing JSON Web Keys (JWK) in R"
date: "`r Sys.Date()`"
output:
  html_document
vignette: >
  %\VignetteIndexEntry{Reading/Writing JSON Web Keys (JWK) in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = "")
```


### RSA / ECDSA keys

JSON Web Keys (JWK) is a format specified in [RFC7517](https://tools.ietf.org/html/rfc7517) for storing RSA/EC/AES keys in a JSON based format. It can be used to import/export such keys in the brower using the new [W3C WebCryptoAPI](https://www.w3.org/TR/WebCryptoAPI/).

The `jose` package makes it easy to read/write such keys in R for use with JWT or any other functionality from the `openssl` package.


```{r}
library(openssl)
library(jose)

# Generate a ECDSA key
key <- openssl::ec_keygen()
jsonlite::prettify(write_jwk(key))

# Use public key
pubkey <- as.list(key)$pubkey
json <- write_jwk(pubkey)
jsonlite::prettify(json)

# Read JWK key
(key2 <- read_jwk(json))
identical(key, key2)
```


### AES/HMAC keys

JWT also specifies a format for encoding AES/HMAC secrets. Such secret keys are simply raw bytes. 

```{r}
# Random secret
(key <- rand_bytes(16))
(jwk <- write_jwk(key))
read_jwk(jwk)
```
