---
title: "Encoding/Decoding JSON Web Tokens (JWT) in R"
date: "`r Sys.Date()`"
output:
  html_document
vignette: >
  %\VignetteIndexEntry{Encoding/Decoding JSON Web Tokens (JWT) in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = "")
```

JavaScript Object Signing and Encryption (JOSE) consists of a set of specifications for encryption and signatures based on the popular JSON format. This is work in progress, the IETF [jose workgroup](https://tools.ietf.org/wg/jose/) usually has the latest information. 

 - [RFC7515](https://tools.ietf.org/html/rfc7515): JSON Web Signature (JWS)
 - [RFC7516](https://tools.ietf.org/html/rfc7516): JSON Web Encryption (JWE)
 - [RFC7517](https://tools.ietf.org/html/rfc7517): JSON Web Key (JWK)
 - [RFC7518](https://tools.ietf.org/html/rfc7518): JSON Web Algorithms (JWA)
 - [RFC7519](https://tools.ietf.org/html/rfc7519): JSON Web Token (JWT)
 
The `jose` package implements some of these specifications, in particular for working with JSON web tokens and keys.

### JSON Web Token: HMAC tagging

The most common use of JSON Web Tokens is combining a small payload (the 'claim') with a HMAC tag or RSA/ECDSA signature. See also [https://jwt.io](https://jwt.io) for short introduction. 

```{r}
library(openssl)
library(jose)

# Example payload
claim <- jwt_claim(user = "jeroen", session_key = 123456)

# Encode with hmac
key <- charToRaw("SuperSecret")
(jwt <- jwt_encode_hmac(claim, secret = key))

# Decode 
jwt_decode_hmac(jwt, secret = key)
```

The decoding errors if the tag verification fails.

```{r error=TRUE}
# What happens if we decode with the wrong key
jwt_decode_hmac(jwt, secret = raw())
```

### JSON Web Token: RSA/ECDSA signature

Similarly, we can use an RSA or ECDSA key pair we to verify a signature from someone's public key.

```{r}
# Generate ECDSA keypair
key <- ec_keygen()
pubkey <- as.list(key)$pubkey

# Sign with the private key
(jwt <- jwt_encode_sig(claim, key = key))

# Decode and verify using the public key
jwt_decode_sig(jwt, pubkey = pubkey)
```

Again decoding will error if the signature verification fails.

```{r error = TRUE}
wrong_key <- ec_keygen()
jwt_decode_sig(jwt, pubkey = wrong_key)
```


The spec also describes methods for encrypting the payload, but this is currently not widely in use yet.

### Reserved jwt-claim names

You can include custom fields in your jwt payload, but the spec names a few [registered claims](https://datatracker.ietf.org/doc/html/rfc7519#section-4.1) that are reserved for specific uses.

 - `iss` (Issuer): the principal that issued the JWT.
 - `sub` (Subject): the principal that is the subject of the JWT.
 - `aud` (Audience): the recipients that the JWT is intended for.
 - `exp` (Expiration Time): the expiration time on or after which the JWT must not be accepted.
 - `nbf` (Not Before): the time before which the JWT must not be accepted.
 - `iat` (Issued At): the time at which the JWT was issued.
 - `jti` (JWT ID): a unique identifier for the JWT.
 
Each of these are optional, by default only `iat` is set. The `jwt_claim()` function will automatically do basic validation when you set additional fields from this list. For any other fields you can use any value. For example:

```{r}
# Note that this token expires in 1 hour!
myclaim <- jwt_claim(
  iss = "My webapp",
  exp = Sys.time() + 3600,
  myfield = "Some application logic",
  customer = "a cow"
)
(jwt <- jwt_encode_sig(myclaim, key = key))
```

The decode functions will automatically verify that the token has not expired, and error otherwise:

```{r}
jwt_decode_sig(jwt, pubkey = pubkey)
```


### Where is the JSON

The jwt payloads consists of a head, body and signature which are separated with a dot into a single string. Both the header and body are actually `base64url` encoded JSON objects.

```{r}
(strings <- strsplit(jwt, ".", fixed = TRUE)[[1]])
cat(rawToChar(base64url_decode(strings[1])))
cat(rawToChar(base64url_decode(strings[2])))
```

However you should never trust this information without verifying the signature. This is what the `jwt_decode` functions do for you.
