---
title: "Encoding/Decoding JSON Web Tokens (JWT) in R"
date: "`r Sys.Date()`"
output:
  html_document
vignette: >
  %\VignetteIndexEntry{Encoding/Decoding JSON Web Tokens (JWT) in R}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = "")
```

JavaScript Object Signing and Encryption (JOSE) consists of a set of specifications for encryption and signatures based on the popular JSON format. This is work in progress, the IETF [jose workgroup](https://tools.ietf.org/wg/jose) usually has the latest information.

 - [RFC7515](https://tools.ietf.org/html/rfc7515): JSON Web Signature (JWS)
 - [RFC7516](https://tools.ietf.org/html/rfc7516): JSON Web Encryption (JWE)
 - [RFC7517](https://tools.ietf.org/html/rfc7517): JSON Web Key (JWK)
 - [RFC7518](https://tools.ietf.org/html/rfc7518): JSON Web Algorithms (JWA)
 - [RFC7519](https://tools.ietf.org/html/rfc7519): JSON Web Token (JWT)
 
The `jose` package implements some of these specifications, in particular for working with JSON web tokens and keys.

### JSON Web Token: HMAC tagging

The most common use of JSON Web Tokens is combining a small payload (the 'claim') with a HMAC tag or RSA/ECDSA signature. See also [https://jwt.io](https://jwt.io) for short introduction.

```{r warning=TRUE}
library(openssl)
library(jose)

# Example payload
claim <- jwt_claim(user = "jeroen", session_key = 123456)

# Encode with hmac
key <- charToRaw("SuperSecret")
(jwt <- jwt_encode_hmac(claim, secret = key))

# Decode
jwt_decode_hmac(jwt, secret = key)
```

The decoding errors if the tag verification fails.

```{r error=TRUE}
# What happens if we decode with the wrong key
jwt_decode_hmac(jwt, secret = raw())
```

## Starting v1.0.1 expiration time can be set and check

It can be set at `jwt_encode|decode_*` by passing the argument `exp = <seconds>`. For back compatibilty, parameter is `NULL` by default and raises a warning indicating that expiracy is not checked.

```{r}
# Create and validate 1 minute HMAC tokens
lifetime <- 60
sig <- jwt_encode_hmac(claim, key, exp = lifetime)
jwt_decode_hmac(sig, key, exp = lifetime)
```

If expiration is exceeded `error` is thrown.

```{r error=TRUE}
# Create and validate 1 second HMAC tokens
lifetime <- 1
sig <- jwt_encode_hmac(claim, key, exp = lifetime)
sleep(2) # Expire token
jwt_decode_hmac(sig, key, exp = lifetime)
```


### JSON Web Token: RSA/ECDSA signature

Similarly, we can use an RSA or ECDSA key pair we to verify a signature from someone's public key.

```{r}
# Generate ECDSA keypair
key <- ec_keygen()
pubkey <- as.list(key)$pubkey

# Sign with the private key
(jwt <- jwt_encode_sig(claim, key = key))

# Decode and verify using the public key
jwt_decode_sig(jwt, pubkey = pubkey)
```

Again decoding will error if the signature verification fails.

```{r error = TRUE}
wrong_key <- ec_keygen()
jwt_decode_sig(jwt, pubkey = wrong_key)
```


The spec also describes methods for encrypting the payload, but this is currently not widely in use yet.

### Where is the JSON

The jwt payloads consists of a head, body and signature which are separated with a dot into a single string. Both the header and body are actually `base64url` encoded JSON objects.

```{r}
(strings <- strsplit(jwt, ".", fixed = TRUE)[[1]])
cat(rawToChar(base64url_decode(strings[1])))
cat(rawToChar(base64url_decode(strings[2])))
```

However you should never trust this information without verifying the signature. This is what the `jwt_decode` functions do for you.
